%Background of project and the significance of project.
%To be included in main file using \input{file}
\section{Background and Significance}
Machine learning is defined as the science of getting computers to act without being explicity asked. This is achieved by the development of computer programs that can teach themselves to grow and change when exposed to different sets of data. There are two traditional types of machine learning algorithms: Batch learning algorithms and on-line machine learning algorithms. Batch learning algorithms require a set of predefined training data that is shaped over the period of time to train the model that the algorithm is running on. On-line learning uses an initial guess model that forms co-variates from that initial guess then passes them through the algorithm to form an evolved model a new set of covariates are formed from the evolved model and then fed back to make a new prediction. The loop runs continuously so that the evolved model is constantly growing and learning to adapt to certain situations. Dr. Rhinelander's research is concerned with on-line machine learning algorithms therefore the drone we are developing will configured to adapt with these algorithms. 

Quadrotor drones have been on the rise in popularity in the last several years due to their simplistic mechanical design and many practical uses. The application of these drones vary from a hobbyist flying around their neighbourhood to military personnel carrying out high risk missions. A video recording device of some sort is generally attached to the drone and the video feed is relayed to a basesation for the operator to gain a field of view (FOV) of an area of interest. Having the capability to have a continuous video feed allows the drone to be used for many practical applications including but not limited to: Traffic condition monitoring and surveillance missions. While these drones are very sophisticated and advanced devices they are are missing one aspect that is very important to further Dr. Rhinelanders research: They are not totally configurable. 

As mentioned, Dr.Rhinelanders research is concerned with on-line machine learning algorithms and without a platform that is completely configurable his research would be limited. Before the machine learning algorithms are implemented onto the drone it must first be able to be controlled. This is where we come in, we have been tasked by Dr. Rhinelander to develop a flight controller that recieves control inputs over Wi-Fi. \textbf{\textit{Having a completely open source flight controller will allow for the addition of the machine learning algorithms to the flight controller software so that the drone can learn to partially, and eventually fully fly on it's own and make intelligent decisions.} }