\section{References}

\begin{enumerate}

\item "Server and Client between PC and Raspberry Pi." Python - Server and Client between PC and Raspberry Pi - Raspberry Pi Stack Exchange. N.p., n.d. Web. 27 Mar. 2017. <http://raspberrypi.stackexchange.com/questions/13425/server-and-client-between-pc-and-raspberry-pi>.

 \item "Activating Electronic Speed Control with Arduino." Electrical Engineering Stack Exchange. N.p., n.d. Web. 27 Mar. 2017. <http://electronics.stackexchange.com/questions/24826/activating-electronic-speed-control-with-arduino>.
 
 \item "Enable I2C Interface on the Raspberry Pi." Raspberry Pi Spy. N.p., 02 Nov. 2014. Web. 27 Mar. 2017. <http://www.raspberrypi-spy.co.uk/2014/11/enabling-the-i2c-interface-on-the-raspberry-pi/>.
 
 \item "Arduino - LibraryTutorial." Arduino - LibraryTutorial. N.p., n.d. Web. 27 Mar. 2017. <https://www.arduino.cc/en/Hacking/libraryTutorial>.
 
 \item Townsend, Kevin. "Adafruit 10-DOF IMU Breakout." (2016): n. pag. 14 Sept. 2016. Web. 27 Mar. 2017. <https://cdn-learn.adafruit.com/downloads/pdf/adafruit-10-dof-imu-breakout-lsm303-l3gd20-bmp180.pdf>.
 
 \item "Filtering Sensor Data with a Kalman Filter." Interactive Matter Lab. Interactive Matter Lab, 28 Jan. 2011. Web. 27 Mar. 2017. <http://interactive-matter.eu/blog/2009/12/18/filtering-sensor-data-with-a-kalman-filter/>.
 
 \item "PyQt5 Reference Guide¶." PyQt5 Reference Guide — PyQt 5.8.1 Reference Guide. N.p., n.d. Web. 27 Mar. 2017. <http://pyqt.sourceforge.net/Docs/PyQt5/>.
 
 \item "Python 3.6.1 Documentation." 3.6.1 Documentation. N.p., n.d. Web. 27 Mar. 2017. <https://docs.python.org/3/>.
 
 \item "IBM Knowledge Center." IBM Knowledge Center. N.p., n.d. Web. 27 Mar. 2017. <https://www.ibm.com/support/knowledgecenter/ssw_ibm_i_71/rzab6/howdosockets.htm>.

\end{enumerate}